---
title: "Introduction to HW 3 Vig"
author: "Sidonia Zinky"
date: "2018 March"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"Introduction to HW 3 Vig"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### MISC CONTENT (function 6)
## Function 6
[even though it has a higher number than others, it is the simpliest, so it is here first - other functions build off this concept]
```{r}

func6 <- function(x){
  
  tryCatch(stopifnot(is.numeric(x)), error=function(e){print("not numeric")})
  tryCatch(stopifnot(is.finite(x)), error=function(e){print("not finite")})
  tryCatch(stopifnot(length(x)!=0), error=function(e){print("has 0 length")})
  tryCatch(stopifnot(!is.nan(x)), error=function(e){print("NA or NAN")})
  tryCatch(stopifnot(!is.na(x)), error=function(e){print("NA or NAN")})
  
}
func6(2)
func6('a')
func6(Inf)
func6(c(1,2,3))
func6(NaN)
func6(NA)

```

### MEAN VAR SD (functions 1,2,4,5)
## Function 1
Purpose: to compute mean, (population) varience, and (population) SD 
Details: takes in a vector x, returns a list with all those components.
Equations used ...
mean:
$$\mu = 1/n \sum_{i=1}^n x_i$$
pop var:
$$\sigma^2 = (1/n) \sum_{i=1}^n (x_i-\mu)^2$$
SD is square root of the var
``` {r}
x<-rnorm(10)
func1 <- function(x){
  a = sum(x)/length(x)
  b = sum((x-a)^2)/length(x)
  c = sqrt(b)
  return(list(mean=a,var=b,sd=c))
}
func1(x)
```

## Function 2
Same as above but with user checks for non-numeric, infinte, NA, NaN values
``` {r}
x<-rnorm(10)
func2 <- function(x){
  stopifnot(is.numeric(x))
  stopifnot(length(x)!=0)
  stopifnot(is.finite(x))
  stopifnot(!is.na(x))
  stopifnot(!is.nan(x))

  a = sum(x)/length(x)
  b = sum((x-a)^2)/length(x)
  c = sqrt(b)
  return(list(mean=a,var=b,sd=c))
}
func2(x)
```

## Function 4
Purpose: to compute WEIGHTED mean, WEIGHTED (population) varience, and WEIGHTED (population) SD 
Details: takes in a vector x, returns a list with all those components.
Equations used ...
mean:
$$\mu = \sum_{i=1}^n x_i * w_i $$
var:
$$\sigma^2 = \sum_{i=1}^n (x_i - \mu)^2*w_i  $$
sd:
$$\sigma = \sqrt(\sigma^2)  $$
```{r}

x <- c(1,2,3)
p <- c(.25,.25,.5)
d <- data.frame(x,p)
func4 <- function(d)
  {
    a = sum(d$x * d$p)
    b = sum(((d$x - a)^2) * d$p)
    c = sqrt(b)
    return(list(mean=a,var=b,sd=c))

  }
func4orig <- function(d){
  return(
    list(
      weighted.mean(d$x,d$p),
      sum(p * (x - weighted.mean(d$x,d$p))^2),
      sqrt(sum(p * (x - weighted.mean(d$x,d$p))^2))))
}
func4(d)
func4orig(d)

```

## Function 5
Same as above but with user checks for non-numeric, infinte, NA, NaN values
```{r}

x <- c(1,2,3)
p <- c(.25,.25,.5)
d <- data.frame(x,p)
badx <- c(NA,2,3)
badd <- data.frame(badx,p)
func5 <- function(d) {
    
    stopifnot(is.numeric(d$x))
    stopifnot(is.numeric(d$p))
    
    stopifnot(length(d$x)!=0)
    stopifnot(length(d$p)!=0)
    
    stopifnot(is.finite(d$x))
    stopifnot(is.finite(d$p))
    
    stopifnot(!is.na(d$x))
    stopifnot(!is.na(d$p))
    
    stopifnot(!is.nan(d$x))
    stopifnot(!is.nan(d$p))
    
    stopifnot(all.equal(sum(d$p),1))
    
    a = sum(d$x * d$p)
    b = sum(((d$x - a)^2) * d$p)
    c = sqrt(b)
    return(list(mean=a,var=b,sd=c))
    
}
func5orig <- function(d){
  return(
    list(
      weighted.mean(d$x,d$p),
      sum(p * (x - weighted.mean(d$x,d$p))^2),
      sqrt(sum(p * (x - weighted.mean(d$x,d$p))^2))))
}
func5(badd)
func5(d)
func5orig(d)

```
### DISTRIBUTIONS (functions 3,7)
## FUNCTION 3
Maximum likelihood estimation for the gamma distribution with unknown shape parameter and known scale parameter
```{r}

options(warn=-1)
x<-rnorm(10)
func3 <- function(x){
  alpha <- pi
  log <- function(alpha)
    sum(dgamma(x, shape = alpha, log = TRUE))
  interval <- mean(x) + c(-1,1) * 3 * sd(x)
  interval <- pmax(mean(x) / 1e3, interval)

  oout<- optimize(log, maximum = TRUE, interval)
  return (oout$maximum)
}
func3(x)


```

## FUNCTION 7
Maximum likelihood estimation for the any distribution with unknown shape parameter and known scale parameter
Tested here with the gamma distribution.
```{r}

func1 = function(theta, x) dgamma(x, shape = theta, log = TRUE)

func7 <- function(x, func, interval){
  
  f7 <- function(theta, x)
  {sum(func(theta, x))}
  
  oout<- optimize(f7, maximum = TRUE, interval, x=x)
  return(oout$maximum)
}
x1 <- scan(url("http://www.stat.umn.edu/geyer/3701/data/q1p3.txt"))
result7_gamma <- func7(x1,func1,c(0,3))
result7_gamma

```
